Cryptographic assurance of secrecy and fairness in voting

### 2012-12-08 paper/paper.tex
Work on analysis of ballot secrecy

\subsection{After voting}
A publicly-available bulletin board publishes all recorded votes, i.e., the right-hand sides of each cast ballot, including its onion and vote as recorded.
A voter can then verify that her vote was correctly recorded by checking that her receipt matches the information displayed on the bulletin board.

@@

@@

\subsection{Coercion prevention}

\term{Scantegrity} prevents coercion via the manner it uses to encrypt ballots. Once cast, a ballot's
ciphertext is \emph{always public}. A voter can claim that she voted in a particular manner, but
without exposure of the data maintained in Table P -- \term{Scantegrity}'s secret -- the voter has no
way to prove to a third party that the claim is true.

An important point regarding \term{Scantegrity} is that it also relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code bubbles -- to combat vote coercion (i.e., no
one can force a voter to produce a particular receipt, and no one can take a receipt and ably pay
the person for having voted a certain way). This is akin to keeping Table P a secret: the ballots
together \emph{are} Table P, and using special ink allows the codes to be printed without making it
easy for a ballot handler to simple read Table P from the ballots prior to the election.

>>>>

\subsection{After voting}
A publicly-available bulletin board publishes all recorded votes, i.e., the right-hand side of each cast ballot, including its onion and vote as recorded.
A voter can then verify that her vote was correctly recorded by checking that her receipt matches the information displayed on the bulletin board.

@@

Voters must rely on varied auditing authorities to verify this tallying process.

@@

\term{Scantegrity} resists coercion via the manner it uses to encrypt ballots. Firstly, assuming
physical security, without access to Table P or Table R, one cannot predict the confirmation codes
that will be produced by casting a ballot in a particular manner. Secondly, without exposure of the
data maintained in Table P or Table R, a voter has no way to prove to a third party that she has
voted as claimed.

An important point regarding \term{Scantegrity} is that it also relies on a \emph{physical property} -- the
invisible ink used when printing confirmation code bubbles -- to combat vote coercion. This is akin
to keeping Table P a secret: the ballots together \emph{are} Table P, and using special ink allows
the codes to be printed without making it easy for a ballot handler to simple read Table P from the
ballots prior to the election.
